\begin{thebibliography}{99}
\bibitem{RenFutian}
徐吉谦,~任福田.~交通工程总论.~北京：人民交通出版社,~2002:~4-5.
\bibitem{Niuhu}
牛虎.~四阶段法交通需求的局限与非集计模型的发展.~交通标准化,~2007,~12(172):~73-76.
\bibitem{zhenyangli}
Li Zhenyang. Dynamic Left-turn Phase Optimization Using Fuzzy Logic
Control [ PhD Dissertation] Knoxville: University of Tennessee,
Knoxville, 2004.
\bibitem{quan} 全永.~城市交通控制.~北京：人民交通出版社.~1989.
\bibitem{wangqian}王茜.~城市交通信号控制系统特征参数研究.~同济大学硕士学位论文.~2003.
\bibitem{xuekun}薛昆.~十字环形交叉口信号控制理论研究.~同济大学硕士学位论文.~2003.
\bibitem{pp}王璇.~信号交叉口左转保护/许可控制的安全分析和选择规范.~北京交通大学硕士学位论文.~2006.
\bibitem{jixiaojin1}Ji Xiaojin, Prevedouros Panos. Probabilistic Analysis of HCM Delay for Signalized
Intersections. Annual Meeting of the TRB. 2006.
\bibitem{expectation}Park, B. and A. Kamarajugadda. Estimating Confidence Interval for Highway Manual Delay Equation at
Signalized Intersections. Transportation Research Board, CD-ROM,
National Research Council, Washington, D.C., 2003.
\bibitem{interval}Tarko, A. and Z. Tian. Example Analysis and Handling of Uncertainty in HCM with Consideration of
Traffic Diversion. In Transportation Research Record: Journal of the
Transportation Research Board, No. 1852, TRB, National Research
Council, Washington, D.C., pp. 40-46.
\bibitem{analysis}Luttinen, R. T. Uncertainty in Operational Analysis of Two-lane Highways. In Transportation Research
Record: Journal of the Transportation Research Board, No. 1802, TRB,
National Research Council, Washington, D.C., pp. 105-114, 2002.
\bibitem{fuzzy}Ji, X. Uncertainty Analysis of HCM Signalized Intersection Delay Using Fuzzy Set Theory. Proceedings of
ITE District 6 Annual Meeting, Kalispell, MT, July 2005.
\bibitem{sensitivity}Khatib, Z. and M. Kyte. Uncertainty in Projecting the Level of Service of Signalized and Unsignalized
Intersections. Transportation Research Board, CD-ROM, National
Research Council, Washington, D.C., 2001.
\bibitem {jixiaojinlevel}Ji Xiaojin, Prevedouros Panos. Probabilistic Analysis of HCM Models: Case Study of Signalized
Intersections. Annual Meeting of the TRB. 2006.
\end{thebibliography}
